The zero--one laws of Kolmogorov and Hewitt--Savage in categorical probability

### 2020-05-04 categorical-zero-one.tex
edits, added .txt file

\begin{example}
$\CRing_{+}^{\op}$ is \emph{not} causal.
To see this, consider the ring $\mathbb{Z}[\epsilon]/(\epsilon^{2})$.
Elements have the form $a + b\epsilon$, with $a,b\in\bZ$, and multiplication is
defined by the convention $\epsilon^{2} = 0$.
Consider the additive maps given by
\begin{align*}
	f(a + b\epsilon) = {}& b\\
	g(a + b \epsilon) = {}& b\\
	h_{1}(a+ b \epsilon) = {}& a + b \epsilon\\
	h_{2}(a + b \epsilon) = {}& 0
\end{align*}
Since $gf = 0$, it's clear that the hypothesis holds, so if $\CRing_{+}^{\op}$
were causal, we would have the equation
$g(f(h_{1}(x)y)z) = g(f(h_{2}(x)y)z)$ for all
$x,y,z \in \bZ[\epsilon]/(\epsilon^{2})$.
However, this clearly fails if $z = \epsilon$, $y=1$ and $x = \epsilon$.
\todo[inline]{It would be nice to have such an example. But this one doesn't work, since these additive maps are not unit-preserving.}
\end{example}

>>>>

\begin{example}
$\CRing_{+}^{\op}$ is \emph{not} causal.
To see this, consider the ring $\mathbb{Z}[t]$.
Consider the additive maps given by
\begin{align*}
	f(t^{n}) = {}& \begin{cases}t & n \geq 1 \\ 1 & n= 0\end{cases}\\
	g(t^{n}) = {}& \begin{cases}t^{n-1} & n \geq 1 \\ 1 & n = 0 \end{cases}\\
	h_{1}(t^{n}) = {}& t^{n}\\
	h_{2}(t^{n}) = {}& t^{n+1}
\end{align*}
Now $gf(t^{n}) = 1$, $h_{1}(p(t))q(t) = p(t)q(t)$, and
$h_{2}(p(t))q(t) = tp(t)q(t)$.
So it's easy to verify that the hypotehis holds.
If $\CRing_{+}^{\op}$ were causal, we would have
$g(f(h_{1}(p(t))q(t))r(t)) = g(f(h_{2}(p(t))q(t))r(t))$.
But this clearly fails for e.g $p(t)=q(t)=r(t) = t$.
$g(f(h_{1}(1)1)t) = 1$, but $g(f(h_{2}(1)1)t) = t$.

\todo[inline]{It would be nice to have such an example. But this one doesn't
  work, since these additive maps are not unit-preserving.}
\todo[inline]{I've adapted this from the similar example in your reference paper.}
\end{example}
